### 2015-09-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update delco 2012

Water flowrate was measured with a pressure and flow meter combination. The meter consists of a section of 6.35~cm (2.5~inch) cast aluminum pipe with a 0 - 4.1~MPa (0 - 600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.  The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\%  for the pressure sensor~\cite{Akron:2009}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate. The total expanded uncertainty was estimated at $\pm$ 10 %.

@@

The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs.

@@

\begin{sidewaystable}[!ht]
	\centering
	\scriptsize
	\caption{Fire Suppression Fuel masses}
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{lllllcc}
		\toprule[1.5pt]
		Item               & Component		& Quantity		&  Material Description             							&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
		\midrule
		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame 	   &  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
		           	 	   & \multirow{2}{*}{{Mattress}}	    & \multirow{2}{*}{{1 per sofa}}	& \multirow{2}{*}{\parbox{5cm} {Cover: 52~\% Polypropylene, 48~\% Polyester, Filling: 66~\% Polyester Fiber Pad, 34~\% Polyester Fiber  Batting}} & \multirow{2}{*}{{1.83 L X 1.21 W X 0.14 H}}  & \multirow{2}{*}{{14.6}}     \\
		           	 	   &	            &               &                                                          		&                            	&             		& \\[.25cm]
			           	   & Seat Cushion	& 2 per sofa	& 85~\% Urethane Foam, 15~\% Polyester Fiber   				    &  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame   	    &  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
		    			   & Seat Cushion   & 1 per chair   & 85~\% Urethane Foam, 15~\% Polyester Fiber					&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame        &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
		                   & Seat Cushion	& 1 per chair	& 85~\% Urethane Foam, 15~\% Polyester Fiber		            &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
		Carpeting          &				& 22.26 m$^2$	& 100~\% PET Polyester                  						&  3.68 L X 6.05 W  			&  1.44 kg/m$^2$	& 32.2 \\
		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11~mm H    &  0.89 kg/m$^2$    & 19.8 \\
		                   &                &               &                                                               &                               & Total Mass        & 335.6 \\
		\bottomrule[1.25pt]
	\end{tabular}
	\label{tab:Fire_Suppression_Fuel_Masses}
\end{sidewaystable}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
% 	\caption{Sleeper Sofa}
% 	\label{fig:Sleeper_Sofa}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
% 	\caption{Mattress}
% 	\label{fig:Mattress}
% \end{figure}

% \begin{figure}[!ht]
% 	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
% 	\caption{Blue Chair}
% 	\label{fig:Blue_Chair}
% \end{figure}

@@

Spray density experiments were conducted by placing 2.5 ft$^2$ interlocking collector bins across the floor surface area of the burn rooms within each structure. The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building and 12 were in the concrete structure. Table~\ref{tab:spray_density_tests} provides and overview of each individual experiment. In the table, BB stands for the burn building tests while CS stands for the concrete structure tests. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

@@

BB1        &   120              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
BB2        &   120              & 23            & Water  &  Solid Stream       &                    &          \\
BB3        &   120              &               & Water  &  Solid Stream       & 16                 &          \\
BB4        &   120              &               & Water  &  Solid Stream       & 16                 &          \\
BB5        &   120              & 20            & Water  &  Solid Stream       & 16                 &          \\

@@

BB7        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
BB8        &   120              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\

@@

BB10       &   120              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\

@@

BB12       &   120              & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
BB13       &   120              & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB14       &   120              & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB15       &   120              & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB16       &   120              &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
BB17       &   120              & 20            & CAF    &  Solid Stream narrow & 15                &          \\
BB18       &   120              & 10            & CAF    &  Solid Stream mid   &                    &          \\
BB19       &   120              & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
BB20       &   120              &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\
BB21       &   120              &               & CAF    &  Solid Stream back  &                    &          \\
CS1        &   115,75           &               & Water  &  Solid Stream       &                    &          \\
CS2        &   120,115          & 18            & Water  &  Solid Stream       &                    &          \\

@@

CS4        &   120,118          & 21            & Water  &  Solid Stream       &                    &          \\
CS5        &   120,118          & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS6        &   120,118          & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS7        &   120,124          & 15            & Water  &  Solid 7/8~in slug  &                    &          \\
CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  &                    &          \\
CS8        &   120,116          & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS9        &   120,116          & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS10       &   120,116          & 16            & Water  &  Solid Stream       &                    &          \\
CS11       &   120,117          & 16            & Water  &  Solid Stream       &                    &          \\

>>>>

Water flowrate was measured with a pressure and flow meter combination. The meter consists of a section of 6.35~cm (2.5~inch) cast aluminum pipe with a 0 - 4.1~MPa (0 - 600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm). The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.  The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\%  for the pressure sensor~\cite{Akron:2009}. The pressure transducer was calibrated with a known analog pressure gauge. The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate. The total expanded uncertainty was estimated at $\pm$ 10~\%.

@@

The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs, carpet, padding, and wood paneling along the southeast corner walls. An image of the fuel arrangement is shown in Fig.~\ref{fig:Furniture_Fuel_Load}. The couches and chairs are setup to mimic a typical seating area with one couch against the south and east wall respectively with each being 0.9~m (36~in) away from the corner. A chair is placed adjecent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}. In total, this fuel package contains approximately 336 kg of fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP). Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.

@@

\begin{sidewaystable}[!ht]
	\centering
	\scriptsize
	\caption{Fire Suppression Fuel masses}
	\renewcommand{\tabcolsep}{1pt}
	\begin{tabular}{lllllcc}
		\toprule[1.5pt]
		Item               & Component		& Quantity		&  Material Description             			&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
		\midrule
		2-seat Sofa        &				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
		           	 	   & Mattress	    & 1 per sofa	& Cover: 52~\% PP, 48~\% PET,                   &  1.83 L X 1.21 W X 0.14 H     &  14.6             & \\
		           	 	   &                &               & Filling: 66~\% PET Pad, 34~\% PET Batting     &                               &                   & \\
			           	   & Cushion    	& 2 per sofa	& 85~\% PU Foam, 15~\% PET Fiber   				&  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
		Blue Chair         &				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
		    			   & Cushion        & 1 per chair   & 85~\% PU Foam, 15~\% PET Fiber				&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
		Blue/Green Chair   & 				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame    &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
		                   & Cushion    	& 1 per chair	& 85~\% PU Foam, 15~\% PET Fiber		        &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
		Paneling           &				& 8 panels		& Medium density fiberboard                     &  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
		Carpeting          &				& 22.3 m$^2$	& 100~\% PET                  					&  3.68 L X 6.05 W  			&  32.2				& 32.2 \\
		Carpet Padding     &				& 22.3 m$^2$	& PU                       	 				    &  3.68 L X 6.05 W X 11~mm H    &  19.8			    & 19.8 \\
		                   &                &               &                                               &                               & Total Mass        & 335.6 \\
		\bottomrule[1.25pt]
	\end{tabular}
	\label{tab:Fire_Suppression_Fuel_Masses}
\end{sidewaystable}

@@

Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure. The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted. Water flowed for a specified duration and upon completion the bins were removed from the structure. Each bin was then weighed to quantify the impact of nozzle location and spray pattern. Thirty-three spray density tests were conducted; 21 were in the burn building and 12 were in the concrete structure. Table~\ref{tab:spray_density_tests} provides an overview of each experiment. In the table, BB stands for the burn building tests while CS stands for the concrete structure tests. For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.

@@

BB1        &   123              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
BB2        &   122              & 23            & Water  &  Solid Stream       &                    &          \\
BB3        &   119              &               & Water  &  Solid Stream       & 16                 &          \\
BB4        &   118              &               & Water  &  Solid Stream       & 16                 &          \\
BB5        &   118              & 20            & Water  &  Solid Stream       & 16                 &          \\

@@

BB7        &   118              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
BB8        &   119              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\

@@

BB10       &   127              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\

@@

BB12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
BB13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
BB17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream narrow & 15                &          \\
BB18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream mid   &                    &          \\
BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\
BB21       &   120 / 60cfm      &               & CAF    &  Solid Stream back  &                    &          \\
CS1        &   115              & 7             & Water  &  Solid Stream       &                    &          \\
CS2        &   115              & 18            & Water  &  Solid Stream       &                    &          \\

@@

CS4        &   118              & 21            & Water  &  Solid Stream       &                    &          \\
CS5        &   118              & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS6        &   118              & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS7        &   125              & 16            & Water  &  Solid 7/8~in slug  &                    &          \\
CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  & 18                 &          \\
CS8        &   116              & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS9        &   116              & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\
CS10       &   116              & 16            & Water  &  Solid Stream       &                    &          \\
CS11       &   117              & 16            & Water  &  Solid Stream       &                    &          \\
